Modularizing Street Map Generation \\ \vspace{8pt} \large An Adventure in Tensors

### 2013-12-12 paper/paper.tex
added introduction and goals from google doc

\newcommand{\sqmat}[4]{\ensuremath{
    \left(\begin{array}{cc}
        #1 & #2 \\
        #3 & #4
    \end{array}\right)}}
\newcommand{\mkvec}[2]{\ensuremath{
    \left(\begin{array}{c}
        #1 \\
        #2 \\
    \end{array}\right)}}
\newcommand{\pt}{\textbf{p}}
\newcommand{\todo}[1]{\begin{center}\fbox{\parbox{150pt}{#1}}\end{center}}

@@

\section{Introduction}

\section{Existing Work}

\section{Our Goals}

@@

\subsection{User-Generated Constraints}
We begin with a JSON parser, which accepts linear and radial constraints.
Constraints must be input with their type, linear or radial, in addition to
their position in the domain (in the form of x and y coordinates), and finally,
if the constraint is linear, it’s direction in radians and magnitude. In
addition, the executable will accept width and height parameters representing
the size of the domain to build street maps on. Together, the JSON constraints
and width/height parameters form the initial input data that will next be used
to form tensor fields.

>>>>

\newcommand{\sqmat}[4]{\ensuremath{
    \left(\begin{array}{cc}
        #1 & #2 \\
        #3 & #4
    \end{array}\right)}}
\newcommand{\mkvec}[2]{\ensuremath{
    \left(\begin{array}{c}
        #1 \\
        #2 \\
    \end{array}\right)}}
\newcommand{\pt}{\textbf{p}}
\newcommand{\todo}[1]{\begin{center}\fbox{\parbox{150pt}{#1}}\end{center}}
\def \cpp {C\nolinebreak[4]\hspace{-.05em}\raisebox{.4ex}{\tiny\bf ++}~}

@@

\section{Introduction}
Visual artists often face the time-consuming task of generating extensive,
realistic scenes by hand for movies and video games. However, the apparent
randomness found in systems like street layouts can be modelled effectively
with a variety of mathematical algorithms, giving rise to the growing field of
procedural generation. In this paper we will discuss an algorithm using tensor
fields, from [Chen], to generate realistic city street maps. To facilitate the
generation of aesthetically pleasing maps which fit an artist's requirements,
we implement a simple system of user-specified constraints to allow the user to
shape the resulting street map to fit their needs.

\section{Existing Work}
\textit{Interactive Procedural Street Modelling} \cite{chen} introduces a novel
new concept of using tensor fields to model realistic street layouts. They 
offer
a well-defined pipeline of mathematical operations to go from simple user
inputs to a final street graph. They also implement a number of operations to
modify the street graph more granularly once it has been generated, such as
removal of roads and retracing of the roads in a defined region with a new
tensor field. The mathematical concepts fundamental to the procedural
generation algorithm are covered thoroughly and clearly.

While all of the information presented in the paper to be very well-formulated
and informative, we found the provided implementation of the described
algorithm more difficult to grasp. The large quantity of \cpp code necessary to
implement the full-featured interactive system provided by Chen et al. made it
difficult for us to thoroughly understand the constituent components such that
we would be able to modify or extend the existing code.

\section{Our Goals}
We thought we could use the power and expressiveness of a functional language 
to produce a more modular, extensible, and readable implementation of the core 
of the algorithm described in Chen et al. which would provide a more 
accessible starting point for later work to build off of. While we sacrifice 
the performance offered by the \cpp implementation, which is closely tied to
OpenGL, we contend that the gains in programmer productivity will more than
make up for this deficit. While a production implementation of such a pipeline
should certainly be implemented with efficiency in mind, we believe that, in
the process of investigating new algorithms, the ease with which the
implementor can translate an idea or mathematical concept into proof-of-concept
code is of the utmost importance. Later in the paper, we will assess our
success in achieving these goals.

@@

\subsection{User-Generated Constraints}
We begin with a JSON parser, which accepts linear and radial constraints.
Constraints must be input with their type, linear or radial, in addition to
their position in the domain (in the form of $x$ and $y$ coordinates), and
finally, if the constraint is linear, it’s direction in radians and magnitude.
In addition, the executable will accept width and height parameters
representing the size of the domain to build street maps on. Together, the JSON
constraints and width/height parameters form the initial input data that will
next be used to form tensor fields.
